{memer}: an R interface to the MEME Suite

### 2020-06-11 manuscript.Rmd
small updates

@@

# Future developments:
 - Additional meme suite tools
 - better support for PSP generation

>>>>

Data from MEME Suite tools can be underutilized because HTML interface?
 - HTML is great human-readable reporting interface
 - `memer` allows customized reporting.

Bioconductor is deprecating PWMEnrich (~AME) and MotIV (~TomTom), `memer` can fill the gap and add additional value.

@@

# Future developments:
 - Additional meme suite tools
 - better support for PSP generation
 - Better support for amino-acid sequence usage (please contact us with feature requests)
